---
title: "cross_validation"
author: "Lulu Zhang"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

no test to see which one is statistically significant bc no pvalue here

use root mean square error model 
```{r}
rmse(linear_mod, test_df)

rmse(smooth_mod, test_df)

rmse(wiggly_mod, test_df)
```

on avg, the squared distance is about 0.8 for the linear model
for the smooth model, its abut 03
wiggly model is about 0.38

no pvalue saying which model is stat sig worse or better

this gives us an idea of how well the testing data 
pick the one that is the best with the testing data
putting mor ein model, will always make rmse go down for training data


## Do this all using `modelr`

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
```

how many times do you want to do this cross validation?
it generates 100 training testing pairs and saves into df


one note about resample...

in my cv_df, pulll out training, convert 1st element, gives table with 79 rows that have ids and x and y var
in this training split

datasets change when you change the training split 

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
```


```{r}
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble
```


convert all of these to datasets
take training ds, map across training column, converitn all of them to df, same for testing column

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

try fitting the linear model to all of these...

```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))
```

map2 gives you a first and second column
map just gives you one column



```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


## example: child growth

```{r}
child_growth = read_csv("./nepalese_children.csv")

child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```


```{r}
child_growth =
  child_growth %>% 
  mutate(weight_cp = (weight > 7) * (weight - 7))
```

```{r}
linear_mod    = lm(armc ~ weight, data = child_growth)
pwl_mod    = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```

```{r}
child_growth %>% 
  gather_predictions(linear_mod, pwl_mod, smooth_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(~model)
```

```{r}
cv_df =
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
         pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
         smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

